---
title: "p8105_hw1_lj2607"
output: github_document
date: "2024-09-21"
---

Problem 1

```{r}
#load dataset penguis

data("penguins", package = "palmerpenguins")
```

```{r}
#check the first 10 rows in data

head(penguins,10)
```


```{r}
#check the size of dataset

nrow(penguins)
ncol(penguins)
```

```{r}
#list valuable variable in th dataset

penguins = janitor::clean_names(penguins)
names(penguins)

```

```{r}
#calculate the mean flipper length after cleaning NA values
mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)

# Print the result
mean_flipper_length
```

```{r}
# check the summary of dataset
summary(penguins)
```

The penguins dataset includes 344 observations rows and 8 columns across three species (Adelie, Chinstrap, and Gentoo) from three islands (Biscoe, Dream, and Torgersen) collected between 2007 and 2009. Key measurements include sex, bill length (ranging from 32.1 mm to 59.6 mm), bill depth (13.1 mm to 21.5 mm), flipper length (172 mm to 231 mm with mean equal to 200.9), and body mass (2700 g to 6300 g). There are some missing values in the dataset.

```{r}
#load package ggplot2
library(ggplot2)

#make a scatterplot with X as bill_length_mm and Y as flipper_length_mm and color points using Species variable
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatterplot_penguins.png")
```

Problem 2

```{r}
# load package tidyverse
library(tidyverse)

# create dataframe based on requirment
random_sample = tibble(
  norm = rnorm(10),
  vec_logical = c(norm >0),
  vec_char = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor = factor(rep(c("1", "2", "3"), length.out = 10))
)
random_sample
```

```{r}
#take the mean of 10 random sample
mean(pull(random_sample,var = norm))
```

```{r}
#take the mean of 10 logical vector
mean(pull(random_sample,var = vec_logical))
```

```{r}
#take the mean of 10 character vector
mean(pull(random_sample,var = vec_char))
```

```{r}
#take the mean of 10 factor vector
mean(pull(random_sample,var = vec_factor))
```

```{r}
#take the mean of 10 factor vector as logical variable
mean(as.numeric(pull(random_sample,var = vec_logical)))

#take the mean of 10 factor vector as numeric variable
mean(as.numeric(pull(random_sample,var = vec_factor)))

#take the mean of 10 character vector as numeric variable
mean(as.numeric(pull(random_sample,var = vec_char)))
```

